Untitled

### 2018-08-20 PaperCode.Rmd
Triple prediction model
This update has no bootstrap model but uses a normal logistic regression, to predict three variables.

```{r}
#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass = CountryAffordClass, ID, LowUse, Homes)

@@

  LADMean %>%
  ggplot(aes(x= AffordRank, y = LowUseRank, colour = LowUseAfford)) + geom_point() +
    geom_vline(xintercept  = 0.5)+
    geom_hline(yintercept = 0.5) +
    labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
  SaveFig("LowUseAffordcolour.pdf")

@@

@@

LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
 # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,3))

@@

@@

MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

@@

@@

 test2 <- test %>%
   select(LAD11CD, Predres, counts) %>%
   spread(key = Predres, value = counts, fill = 0) %>%
   mutate(FractCorrect = `TRUE`/200) %>%
   left_join(LADMean %>% select(LAD11CD, HighValCount, LAD11NM, AffordRank, LowUseRank, LowUseAfford, TourismDensity)) %>%
   left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian) %>%
   left_join(LostLowUse)

@@

Boot MSOA

```{r}
FormulaMSOA <- as.formula(Reference ~ TourismDensity + AffordRatio)

set.seed(1983)
TestResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighLUP")

BootVoteModel <- 1:100 %>% map(~{ 
   print(.x)
    trainrows <- rsample2caret(TestResample)$index[[.x]]
    testrows <-  rsample2caret(TestResample)$indexOut[[.x]]

    test <- MSOAModelData %>% 
      mutate(Reference = HighLUP) %>% 
      BootstrapResampledModelPerf(., trainrows, testrows, FormulaMSOA ) # creates a dataframe out predictions

    PredVect <- factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE"))

  ConfOut <- MSOAMean %>% mutate(Reference = factor(HighLUP, levels = c("FALSE", "TRUE")))  %>% 
    slice(testrows) %>% pull(Reference) %>%
    confusionMatrix( data = PredVect, reference = .)

      ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
      mutate(sample = .x)

rm(FormulaMSOA)

test<- MSOAModelData %>% group_by(ID)%>% summarise(counts= n())

@@

PredictData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapAllLADs") )%>%  
  MeanModelData(., "LAD")

FormulaBootLAD<- ModelFormula <- as.formula(Reference ~ TourismDensity + AffordRatio)

trainrows <- 1:nrow(LADModelData)

BootstrapLADModels <- LADModelData %>% 
  mutate(Reference = as.factor(HighVal)) %>% 
  BootstrapResampledModelPerf(., trainrows, 0 , FormulaBootLAD, ModsOut = TRUE ) # creates a list of models

VoteResults<- BootstrapLADModels %>% map(~{
 preds2 <- tibble(x = predict(.x, newdata = PredictData, type = "response" )>0.5)

}) %>% bind_cols() %>% rowSums(.) %>%
  tibble(Votes = .) %>%
  mutate(Prob = Votes/length(BootstrapLADModels), 
         Class = Prob>0.5,
         LAD11CD = PredictData$LAD11CD) %>%
  left_join(., AdjustmentProb, by = "Votes") %>%
  mutate(AdjustedProb = (Prob-0.5)*ConfProb+0.5)

WholeCountry <- LADMean %>% select(LAD11CD, Votes = HighValCount) %>%
  mutate(Prob = Votes/max(Votes), #a bit dodgey to do that but I know there are 100% outcomes
         AdjustedProb = Prob,
         Class = Prob>0.5) %>% #The addujsted probability of the collected dataset is simply the probability that the medianHOMes<MedianLUPs so no change us needed
  bind_rows(VoteResults) %>%
  left_join(MSOAtoLAD %>% group_by(LAD11CD, LAD11NM) %>% summarise(Pop = sum(Pop))) %>%
  mutate(Diff = Prob-AdjustedProb)

@@

PopAffected <- ((PopAffected >WholeCountry$AdjustedProb)*WholeCountry$Pop) %>%  t %>% rowSums(.) %>%
  tibble(InvestmentPop = .) %>%
  mutate(PopPerc = InvestmentPop/ sum(WholeCountry$Pop))

PopAffected %>% ggplot(aes(x = PopPerc)) + geom_density() +
  labs(title ="Estimate percentage of the Population living in areas with high LUP values",
       x = "Population percentage")
SaveFig("PopulationHighLUP.pdf")

@@

#Predict MSOA High LUP

@@

PredictDataMSOA <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapAllLADs") )%>%  
  MeanModelData(., "MSOA")

FormulaMSOAPredAll <- as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2)

PredictAllMSOAMod <- MSOAMean %>% 
  mutate(Reference = as.factor(HighLUP))  %>%
      glm(formula =FormulaMSOAPredAll , data = ., family=binomial(link='logit'))

summary(PredictAllMSOA)

MSOAWholeCountry <- tibble(HighLUP = predict(PredictAllMSOAMod, newdata = PredictDataMSOA, type = "response" )>0.5,
                  MSOA11CD = PredictDataMSOA$MSOA11CD) %>%
  mutate(HighLUP = as.factor(HighLUP)) %>%
  bind_rows(select(MSOAMean, MSOA11CD, HighLUP))

#Plot Model Outputs

##LAD model
```{r}
LADshapfile <-file.path(basewd,"ShapeFiles", "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain",
                        "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain.shp")

LADShape2 <- LADShape %>% left_join(WholeCountry, by = c("lad14cd" = "LAD11CD")) %>%
  filter(!is.na(Class))

ggplot(LADShape2) +
  geom_sf(aes(fill = Class)) + 
  labs(title = "Local Authorities classified as having predominently high value LUPs")
SaveFig("EWHighValMap.pdf")

@@

MSOAshapefile <-file.path(basewd,
                         "/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
                         "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp")

MSOAShape <- st_read(MSOAshapefile) %>% left_join(MSOAWholeCountry, by = c("msoa11cd" = "MSOA11CD")) %>%
  filter(!is.na(HighLUP))

ggplot(MSOAShape2) +
  geom_sf(aes(fill = HighLUP, colour = HighLUP)) + 
  labs(title = "Local Authorities classified as having above the median percentage of LUPs")
SaveFig("EWHighLUPMap.pdf")

>>>>

setwd(file.path(basewd, "BootstrapAffordQuartiles"))
BootStrapQuartiles <- LoadBootstrapData()

#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass = CountryAffordClass, ID, LowUse, Homes)

@@

  LADMean %>%
  ggplot(aes(x= AffordRank, y = LowUseRank, colour = LowUseAfford)) + geom_point() +
    geom_vline(xintercept  = 0.5)+
    geom_hline(yintercept = 0.5) +
    labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
  #SaveFig("LowUseAffordcolour.pdf")

@@

#Empty Homes tax

Calculates the vancouver tax

welsh data comes from 
https://statswales.gov.wales/Catalogue/Local-Government/Finance/Council-Tax/Levels/counciltaxlevels-by-billingauthority-band

```{r}
setwd(DataFolder)
WelshTax <- read_csv("WelshCTax.csv", skip = 6, n_max = 23) %>%
  select(-X1) %>%
  mutate(CouncilTax = rowSums(.[-1])*1000) %>%
  rename(LAD11NM = X2) %>%
  left_join(., MSOAtoLAD %>% 
              select(LAD11CD, LAD11NM) %>%
              distinct(LAD11NM, .keep_all = T)) %>%
  filter(!is.na(LAD11CD)) %>%
    select(LAD11CD, CouncilTax)

QRC2017 <- read_xlsx("QRC4-2017-2018.xlsx", sheet = 2, skip = 2) %>%
  select(3:4) %>%
  set_names("LAD11CD", "CouncilTax") %>%
  mutate(CouncilTax = CouncilTax*1000) %>%
  bind_rows(WelshTax)

EmptyTax <- LADMean %>% 
  left_join(., QRC2017)%>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(Pop = sum(Pop))) %>%
  mutate(EmptyTax = LowUse*LowUseMean*.01,
         EmptyOfCouncil = EmptyTax/CouncilTax,
         TaxPop = EmptyTax/Pop)

sum(EmptyTax$EmptyTax)/1e6
mean(EmptyTax$EmptyOfCouncil)
median(EmptyTax$EmptyOfCouncil)

mean(EmptyTax$EmptyTax)
median(EmptyTax$EmptyTax)

sum(EmptyTax$EmptyTax)/sum(EmptyTax$CouncilTax)

EmptyTax %>%
  ggplot(aes(x =EmptyOfCouncil)) + geom_density() +
  coord_cartesian(x=c(0,0.7)) +
  scale_x_continuous(labels = scales::percent) +
  labs(title = "Distribution of value of Empty homes tax in terms of council tax by local authority", 
       x = "Percent of council tax value")

EmptyTax %>%
  select(EmptyOfCouncil, LAD11NM) %>%
  arrange(EmptyOfCouncil) %>%
  top_n(5,EmptyOfCouncil)

rm(WelshTax);rm(QRC2017)

@@

LADModTab <-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
 # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,3))

LADModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
  slice(c(2,8,10)) %>%
  xtable(., caption="Summary of viable Local authority models",
       label = "tab:LADmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"))

@@

LADMODOut3 <- ExtractClassCoeffs(LADMean, "HighFinance", LADHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
LADMODOut3 %>%  ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut3 %>%  ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

@@

MSOAModTab <- MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

MSOAModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
  slice(c(4)) %>%
  xtable(., caption="Summary of viable MSOA authority models",
       label = "tab:MSOAmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"))

@@

bind_rows(LADMODOut %>% mutate(type = "Financialised LAD"),
          LADMODOut3 %>% mutate(type = "Highly Financialised LAD"),
          LADMODOut2 %>% mutate(type = "High LUP % LAD"),
          MSOAMODOut %>% mutate(type = "High LUP % MSOA")
) %>%
  ggplot( aes(x = term, y = estimate, fill = term)) + geom_boxplot()+
  facet_wrap(~type)+
    theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))
SaveFig("ModelCoeffs.pdf")

@@

 test2 <- test %>%
   select(LAD11CD, Predres, counts) %>%
   spread(key = Predres, value = counts, fill = 0) %>%
   mutate(FractCorrect = `TRUE`/200) %>%
   left_join(LADMean %>% select(LAD11CD, HighValCount, LAD11NM, AffordRank, 
                                LowUseRank, LowUseAfford, TourismDensity,HighVal)) %>%
   left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian) %>%
   left_join(LostLowUse)

@@

@@

PredictData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapAllLADs") ) %>%  
  MeanModelData(., "LAD")

FormulaBootLAD<-as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2)

ModPreds <- c("HighVal", "HighLUP", "HighFinance") %>%
  map(~{

EWMod <- LADMean %>% 
  rename_(Reference = .x )  %>% 
  mutate(Reference = as.factor(Reference)) %>%
      glm(formula = FormulaBootLAD, data = ., family=binomial(link='logit'))

    PredictData  %>%
      predict(EWMod, newdata = ., type = "response" ) %>%
      as.tibble(.) %>% setNames(.x)

}) %>% bind_cols()

EWMod2<-ModPreds %>% mutate_all(funs((.>0.5)*1)) %>%
  mutate_all(funs(ifelse(.==0, 0.2,0.8))) %>%
               mutate(LAD11CD = PredictData$LAD11CD)

WholeCountry <- LADMean %>% select(LAD11CD, HighVal = HighValCount, HighLUP ) %>%
  mutate(HighVal = HighVal/max(HighVal), #a bit dodgey to do that but I know there are 100% outcomes
         HighLUP = ifelse(HighLUP =="TRUE", 1, 0),
                  HighFinance = HighVal*HighLUP) %>% #The addujsted probability of the collected dataset is simply the probability that the medianHOMes<MedianLUPs so no change us needed
  bind_rows(EWMod2) %>%
  left_join(EW2 %>% group_by(LAD11CD, LAD11NM) %>% summarise(Pop = sum(Pop)))

@@

PopAffected <- tibble(HighValPop =  ((PopAffected <WholeCountry$HighVal)*WholeCountry$Pop) %>%  t %>% rowSums(.),
         HighFinancePop =  ((PopAffected <WholeCountry$HighFinance)*WholeCountry$Pop) %>%  t %>% rowSums(.)) %>%
  mutate(PopPerc = HighValPop/ sum(WholeCountry$Pop),
         FinancePopPerc = HighFinancePop/ sum(WholeCountry$Pop))

PopAffected %>% 
  select(PopPerc, FinancePopPerc) %>%
  gather(key, value) %>%
  mutate(key = ifelse(key == "PopPerc", "Financialised", "Highly Financialised")) %>%
  ggplot(aes(x = value)) + geom_density() +
  facet_wrap(~key, scales = "free_x") +
  labs(title ="Estimate percentage of the Population living in areas with high LUP values",
       x = "Population percentage")
SaveFig("PopulationHighLUP.pdf")

quantile(PopAffected$PopPerc,  probs = c(2.5 ,97.5)/100)
quantile(PopAffected$FinancePopPerc,  probs = c(2.5 ,97.5)/100)

@@

#Plot maps

##Model Outputs
```{r}
LADshapfile <-file.path(basewd,"ShapeFiles", "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain",
                        "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain.shp")

LADShape2 <- WholeCountry %>%
  mutate(HighVal = HighVal>0.5,
         HighLUP = HighLUP>0.5,
         HighFinance = HighFinance>0.5) %>% 
  select(LAD11CD:HighFinance) %>%
  gather(key = Type, value = Status, -LAD11CD) %>%
  mutate(Type = case_when(
    Type =="HighFinance" ~ "Highly Financialized",
    Type == "HighLUP" ~"Large LUP percentage",
    Type == "HighVal" ~"Some Financialization"
  ) %>% as.factor(.) %>% fct_relevel("Highly Financialized", after = 2),
  Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)) %>%
  left_join(LADShape,., by = c("lad14cd" = "LAD11CD")
            ) %>% # Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)
  filter(!is.na(Status))

#plot and save
ggplot(LADShape2) +
  geom_sf(aes(fill = Status)) + 
  facet_wrap(~Type)+
  labs(title = "LUP and financialization status in England and Wales") +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
SaveFig("EWHighValMap.pdf")

#Plot LUP perc

@@

LSOAshape <- st_read(LSOAshapedata) %>%
  left_join(DATAdf, by = c("lsoa11cd"="LSOA11CD")) %>% filter(grepl("Kensington and Chelsea",lsoa11nm)|  grepl("Bradford",lsoa11nm),
                             LAD11CD=="E08000032"|LAD11CD=="E09000020")

colourTypes <- c( "0-10" = "#F8766D", 
                    "11-20" = "#A3A500", 
                   "21-30" ="#00BF7D", 
                   "30+" = "#00B0F6")

LowUseColours <- gg_color_hue(4)
names(LowUseColours) <- c( "0-10", "11-20","21-30","30+")

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

LSOAshape %>%
  filter(LAD11CD=="E09000020")%>%
ggplot(.)+  geom_sf(aes(fill = LowuseClass))  +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
  ggtitle("Low Use percentage by LSOA in Kensington and Chelsea")
SaveFig("ChelseaMap.pdf")

LSOAshape %>%
  filter(LAD11CD=="E08000032")%>%
ggplot(.)+  geom_sf(aes(fill = LowuseClass))  +
      scale_fill_manual(values = LowUseColours) +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
  ggtitle("Low Use percentage by LSOA in Bradford")
SaveFig("BradfordMap.pdf")

@@

Not Neccesary

```{r}
# 
# MSOAshapefile <-file.path(basewd,
#                          "/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
#                          "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp")
# 
# MSOAShape <- st_read(MSOAshapefile) %>% left_join(MSOAWholeCountry, by = c("msoa11cd" = "MSOA11CD")) %>%
#   filter(!is.na(HighLUP))
# 
# 
# ggplot(MSOAShape2) +
#   geom_sf(aes(fill = HighLUP, colour = HighLUP)) + 
#   labs(title = "Local Authorities classified as having above the median percentage of LUPs")
# SaveFig("EWHighLUPMap.pdf")
